The Blue Obelisk five years on

### 2011-03-04 paper.tex
First para on OpenSMILES

OpenSMILES.

>>>>

    \subsubsection*{OpenSMILES}

One of the most widely used ways to store chemical structures is the SMILES format (or SMILES string). This is a linear notation depicted by Daylight Information Systems that describes the connection table of a molecule and may optionally encode chirality. Its popularity stems from the fact that it is a compact representation of the chemical structure that is human readable and writable, and is convenient to manipulate (e.g. to include in spreadsheets, or copy from a Wikipedia article).
